Beta to Release Matching: Modeling

### 2020-03-10 poc/matchIt/modeling.Rmd
update the modeling

* Furthermore, experiments $3$ and $4$ (referring to the results of the feature selection, considering the top 10) were the ones that presented the best results, for most of the tested models.

>>>>

* Furthermore, experiments $3$ and $4$ (referring to the results of the feature selection with the stratified sampling, considering the top 5 and top 10, respectly) were the ones that presented the best results, for most of the tested models.
